---
name: Davi Doneda Mittelstadt
# address: 923 Eagle Heights Apt F - 53705 - Madison/WI - United States of America
date: "`r Sys.setlocale('LC_TIME', 'English'); format(Sys.time(), '%B, %Y')`"
address: "Department of Economics, University of Wisconsin-Madison, 1180 Observatory Drive, Rm 7226, Madison, WI 53706"
email: donedamittel@wisc.edu
www: www.davimittelstadt.com
headcolor: "414141"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
library(dplyr)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)

Sys.setlocale("LC_TIME", "English")
```

# Education
```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ thesis,
    "PhD in Economics", "University of Wisconsin-Madison", "Madison/WI, United States", "Aug. 2021 - 2027 (expected)", "Major: Industrial Organization. Committee: Jean-François Houde, Kenneth Hendricks, Karam Kang",
    "MsC Economics", "Pontifical Catholic University - Rio de Janeiro (PUC-Rio)", "Rio de Janeiro, Brazil", "Jan. 2017 - Aug. 2019", "Thesis: Local Content in Brazilian Oil and Gas Auctions (Advisor: Prof. Leonardo Rezende)", 
  # "MsC Economics", "Pontifical Catholic University - Rio de Janeiro (PUC-Rio)", "Rio de Janeiro, Brazil", "Jan. 2017 - Aug. 2019", "The thesis explored the case of Brazilian oil and gas auctions to assess the impact of local content requirements in bidding behavior, allowing for the estimation of its impact on government revenue.",
  "BA in Economics", "Federal University of Rio Grande do Sul (UFRGS)", "Porto Alegre, Brazil", "Mar. 2011 - Dec. 2012", NA, #"GPA: 9.4/10",
  "BA in International Relations", "Federal University of Rio Grande do Sul (UFRGS)", "Porto Alegre, Brazil", "Mar. 2007 - Dec. 2010", NA,  #"GPA: 9.5/10",
) %>% 
  detailed_entries(degree, dates, uni, loc, thesis)
```

# Job Market Paper
```{r job-market-paper}
tribble(
  ~ title, ~ coauthors, ~ conferences,
  "Asymmetric Information and Search Frictions in Auto Loans", "with Bernardus van Doornik (Central Bank of Brazil)", "Conferences: CEA 2026, North American Summer Meeting of the Econometric Society 2026, EARIE 2026"
) %>%
  detailed_entries(
    with = title,
    what = coauthors,
    why = conferences
  )
```

\begingroup\paragraphstyle

**Abstract:** We estimate a structural model of endogenous search and loan size choice to quantify how asymmetric information and search frictions jointly distort the auto loan market. Using administrative data from the Central Bank of Brazil, we observe the universe of loan contracts and, crucially, the specific set of lenders contacted by each borrower. Empirically, we find evidence of adverse selection on the intensive margin: borrowers who demand more credit are significantly riskier. Using instrumental variables, we show that this correlation is not driven by moral hazard, but by adverse selection. Furthermore, borrowers who search more are riskier and face higher interest rates, indicating that riskier borrowers have more incentives to search. On the demand side of our model, borrowers choose loan size and search intensity, with private information over their search costs and willingness to pay. Car dealers can supply quotes at no search cost to the borrower, which shapes how much they search on their own. Riskier borrowers select into search because their higher reservation rates expose them more to rate dispersion. On the supply side, we allow asymmetric lenders to compete over rates with non-linear menus depending on the loan size. Our estimates show that allowing lenders to perfectly observe consumers' private information would increase originations and borrowing. Larger loans make search more attractive, reducing average rates in equilibrium, given that search costs are high. Borrowers also derive significant surplus from the intermediation provided by car dealers, as most of the spread over a frictionless benchmark is the cost of a thin consideration set.

\par\endgroup

# References

```{=latex}
\vspace{2mm}
\noindent%
\begin{tabular}{@{}p{0.31\linewidth}p{0.31\linewidth}p{0.31\linewidth}@{}}
\entrytitlestyle{Jean-François Houde} & \entrytitlestyle{Kenneth Hendricks} & \entrytitlestyle{Karam Kang} \\
\descriptionstyle{Department of Economics\newline University of Wisconsin-Madison\newline \href{mailto:houde@wisc.edu}{houde@wisc.edu}} &
\descriptionstyle{Department of Economics\newline University of Wisconsin-Madison\newline \href{mailto:hendrick@ssc.wisc.edu}{hendrick@ssc.wisc.edu}} &
\descriptionstyle{Department of Economics\newline University of Wisconsin-Madison\newline \href{mailto:kkang57@wisc.edu}{kkang57@wisc.edu}} \\
\end{tabular}
```

# Research Fields

\begingroup\paragraphstyle

Industrial Organization, Banking, Household Finance, Auctions

\par\endgroup


\newpage

# Work Experience

```{r consulting}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Research Assistant", "UW-Madison", NA, "Fall 2023 - Fall 2025", "Supervisors: Prof. Jean-François Houde and Prof. Kenneth Hendricks",  
  "Analyst", "Stone Payments", "Rio de Janeiro, Brazil", "Aug. 2019 - Aug. 2021", "Manager: Prof. Vinicius Carrasco (Chief Economist & Regulatory Affairs Executive Officer, Assistant Professor PUC-Rio)",
  # "Analyst", "Stone Payments", "Rio de Janeiro, Brazil", "Aug. 2019 - Aug. 2021", "Main activities: supporting the company positions regarding regulatory and antitrust issues, using both economic theory and quantitative analysis. Helping business units to evaluate the impact of new products and practices on business metrics using causal inference methods.",
    "Research Assistant", "PUC-Rio", "Rio de Janeiro, Brazil", "Feb. 2019 - Jul. 2019", "Supervisor: Prof. Fabio Miessi",
  # "Research Assistant", "PUC-Rio", "Rio de Janeiro, Brazil", "Feb. 2019 - Jul. 2019", "Main activities: web scraping, cleaning and updating databases.",
    "Research Assistant", "PUC-Rio", "Rio de Janeiro, Brazil", "Jan. 2018 - Dec. 2018", "Supervisor: Prof. Leonardo Rezende",
  # "Research Assistant", "PUC-Rio", "Rio de Janeiro, Brazil", "Jan. 2018 - Dec. 2018", "Main activities: evaluation of a Brazilian Central Bank policy regarding credit cards, web scraping and data cleaning.",
  "Intern (Oct/2011 - Jan/2013), Analyst (tenured) (Feb/2013 - Dec/2016)", "Rio Grande do Sul Development Agency", "Porto Alegre, Brazil", "Oct. 2011 - Dec. 2016", NA
) %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Teaching Experience

```{r teaching}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Teaching Assistant", "UW-Madison", NA, "Fall 2026", "Course: Econ 468 Industrial Organization and Imperfect Competition (undergraduate)",
  "Teaching Assistant", "UW-Madison", NA, "Fall 2026", "Professor: Panle Barwick",
  "Teaching Assistant", "UW-Madison", NA, "Summer 2023", "Course: Econ 521 Game Theory (undergraduate)",
  "Teaching Assistant", "UW-Madison", NA, "Summer 2023", "Professor: David Hansen",
  "Teaching Assistant", "UW-Madison", NA, "Spring 2023", "Course: Econ 301 Intermediate Microeconomics (undergraduate) - Avg. 4.75/5.0",
  "Teaching Assistant", "UW-Madison", NA, "Spring 2023", "Professor: Rasmus Lentz",
  "Teaching Assistant", "UW-Madison", NA, "Fall 2022", "Course: Econ 521 Game Theory (undergraduate) - Avg. 4.71/5.0",
  "Teaching Assistant", "UW-Madison", NA, "Fall 2022", "Professor: Benjamin Bernard",
  "Teaching Assistant", "PUC-Rio", "Rio de Janeiro, Brazil", "Mar. 2018 - Jul. 2018", "Course: Microeconomics (Professional Masters)",
  "Teaching Assistant", "PUC-Rio", "Rio de Janeiro, Brazil", "Mar. 2018 - Jul. 2018", "Course coordinator: Prof. Fabio Miessi",
  "Teaching Assistant", "UFRGS", "Porto Alegre, Brazil", "Mar. 2011 - Oct. 2011", "Course: Calculus I (undergraduate)",
  "Teaching Assistant", "UFRGS", "Porto Alegre, Brazil", "Mar. 2011 - Oct. 2011", "Course coordinators: Prof. Elizabeta Gallicchio and Prof. Jaime Ripoll (Department of Mathematics)",
) %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Research
## Working papers
```{r working-papers}
tribble(
  ~ title, ~ coauthors, ~ conferences,
  "Local Content in Brazilian Oil and Gas Auctions", "with Leonardo Rezende (PUC-Rio)", "Conferences: Brazilian Econometric Society 2023, Midwest Economics Association 2024, IIOC 2024"
) %>% 
  detailed_entries(
    with = title,
    what = coauthors,
    why = conferences
  )
```

# Honors and Awards

```{r awards}
tribble(
  ~ award, ~ institution, ~ date,
  "Mary Sue and Mike Shannon Dissertation Fellowship", "University of Wisconsin-Madison", "Spring 2027",
  "Christensen Graduate Fellowship in Empirical Economics", "University of Wisconsin-Madison", "Spring 2026",
  "Summer Fellowship", "University of Wisconsin-Madison", "Summer 2025",
  "Distinguished Teaching Assistant", "Department of Economics, University of Wisconsin-Madison", "Spring 2023"
) %>% 
  detailed_entries(
    with = award,
    what = institution,
    when = date
  )
```


# Other information

```{r skills}
tribble(
  ~ category, ~ items,
  "Computer Skills", "R, Julia, Git, LaTeX, SQL",
  "Languages", "Portuguese (native), English (fluent), Spanish (advanced), French (intermediate)"
) %>% 
  detailed_entries(
    with = category,
    what = items
  )
```